Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-20 tex/main/manuscript.tex
测试了可以编译新的参考文献
过了一遍引言的文字

\documentclass[9pt, twocolumn, twoside, lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

@@

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.

% tag 引言第一段
% 水资源在人类世的重要性，是支持人类社会发展的基础
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, 
is not only essential for myriad Earth system processes,
but also a key resource supporting development of human societies in various aspects \cite{gleesonIlluminatingWaterCycle2020}.
% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
At the same time, however, human's modification has profoundly influenced water processes 
and related changes may lead to adverse transitions in functions of human-water systems,
along with various development traps. 
% 世界上诸多大河流域都是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展
Facing major challenges of the Anthropocene, many of the world's big river basins are also centres of economy and civilization 
and urgently in need for integrated water resources management toward sustainability. \cite{bestAnthropogenicStressesWorld2019}
% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助
Therefore, understanding the complex relationship between human societies and water resources utilization 
provides underlying supports to development in a coordinated way, at a basin scale.

% tag 引言第二段
% Regime的定义。
Regime is a general term of system’s structure and function 
and one of the most explanatory perspectives when analysis interactions within a coupling system, 
like human and water.
% Regime的转变
Since widespread fluctuating disturbances in social development and natural water resources were out of consideration, 
water utilization regime only will be driven shifting when reorganizations occurred and the tipping points reached.
% Regime过渡性的存在。
As many large river basins had all experienced phases of accelerated water exploitation, over-exploitation of water resource,
and integrated water management, it is a reasonable assumption that existence of a transitional water utilization regime 
corresponds to development of societies. 
% 过渡性有助于理解流域存在的问题
Understanding the transitional nature of water resource regimes, therefore, can help to diagnosis and predict development traps, 
which is crucial for integrated management and coordinated development at a basin scale regard to sustainability.
% 对过渡性的研究还很少
% Despite pervasive and important, there is lacking of formal framework to interpret the water utilization regimes, 
% with much fewer attempts in developing effective methods to detect them and their transitions as well. 
Despite pervasive and important as it is, there is lacking of effective method to detect the water utilization regimes and their shifts, 
with much fewer attempts to develop formal models of its transitions as well.

% Tag 引言第三段
% 作为是古老而常青的现象，前人已经从不同视角刻画了人水关系.
The key to analysis water utilization regimes is to understand the interactions between human societies and water resources, 
which have been depicted from different dimensions, as an ancient but evergreen topic.
% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
Firstly, the most widespread concern is the rising stresses on human societies with regard to water resources.
% 人类取水量增加，不灵活部分增长，尽管社会通过不断发展拥有更强大的调蓄能力，但世界上绝大多数流域都面临着更大的水资源压力。
Even though the stocks of water in increasing artificial reservoirs are helpful to water resources availability, 
highly stressed basins still characterized by high water consumption intensities and a major constraint to socio-economic development,
driven by a significant increase in water extractions and a larger share of inflexible water utilization during the last century.
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018a, qinFlexibilityIntensityGlobal2019}
% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
Secondly, as the need of industrial and ecological developments, tendentiousness of water utilization changed with.
% 尽管主要的用水方式还是农业灌溉，但工业的经济和用水都正在增长，且存在潜在的冲突。
Despite a major water utilization of agricultural irrigation dominating most of the river basins,
there are significant growths and preferential tendentiousness in the economy profits and water consumption regarding industry, 
leading a high potential for conflict between the industrial and agricultural sectors.
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}
% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
Thirdly, since water availability and utilization are inherently regional concerns, patterns of also play an important role.
% 全球总的取水量很少，但缺水地区很多
Although only 10\% of available water is withdrawn on global average, about 30\% of population live in highly water-stressed areas,
where dominated sections regarding water utilization are various. 
\cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}
% 此外，人类活动还在改变这一格局
In addition, human activities are still changing this pattern, 
since positive impacts caused by human interventions mostly occur in upper regions 
whereas aggravated water resources downstream, in many basins around the world.
\cite{veldkampWaterScarcityHotspots2017}
% 将三种视角结合，就是“水资源利用体系”。
Although existing researches have evaluated the aspects of water resource utilization from these different dimensions, 
we still cannot obtain a coherent understanding of regime regard to social development and water utilization, without integrating them.

% tag 讨论最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, by integrating three above mentioned dimensions of water utilization, 
we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale
to give a sketch of relationships between human societies and their water utilization.
% 使用案例研究
Then, by applying this index to the Yellow River Basin, China,
we analysed water utilization regimes and their shifts in this typical basin of anthropogenic impacts, 
with change points detection and contribution decomposition methods following.
% 指出发展困局
In addition, combining model and data analysis, 
we further identify resource and development traps that have been exposed by regimes' shifting.
% 最后总结出一般性框架
Finally, refer to the existing theories, we summarized a general transition framework of water utilization regimes, 
which can be a useful guideline for basins to predict development traps and to develop in a coordinated way.

>>>>

%!BIB program = bibtex
\documentclass[9pt, twocolumn, twoside, lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}

@@

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.

% tag 引言第一段
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects \cite{gleesonIlluminatingWaterCycle2020}. 
% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
At the same time, however, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in various development traps \cite{cummingLinkingEconomicGrowth2018}. 
% 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need for integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}. 
% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
Therefore, understanding the complex relationship between human societies and water resources utilization, and its evolution provides underlying supports to development in a coordinated way, at a basin scale.

% tag 引言第二段
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018a}.
% 人水系统中的水资源功能
Within human-water systems, water have several key functions, the most important of which is supplying for human societies in sustainable development based on a complex structure of water utilization. 
% 水资源利用 regime shift
However, inter-connected human interference, involving water withdrawal, dam constructions and water managements have significantly changed water functions and induced regime shifts in water utilization
\cite{falkenmarkUnderstandingWaterResilience2019}.
% 稳态转换随着社会发展增加
These regime shifts, triggered by gradual or abrupt drivers, are likely to occur more often as societies' development increasing their pressure or stuck in traps at a basin scale.
% Regime 过渡性的存在
As a result, many large river basins had gone through water utilization regimes of accelerated exploitation, over-exploitation, and integrated governance, as such it is a reasonable assumption that there is a transition pattern within regime shifts. 
% 过渡性有助于理解流域存在的问题
Sketching the transition of water utilization regimes, therefore, can help to understand and predict development traps, which is crucial for integrated management and coordinated development towards sustainability at a basin scale.
% 对过渡性的研究还很少
Despite pervasive and important, there is still lacking of effective method to define the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transition phases as well.

% Tag 引言第三段
% 前人已经从不同维度刻画了人水关系.
Development of societies by using water resources has been going on for at least thousands of years. Although its regime shifts and transition phases are not fully understood yet, water utilization has been depicted and studied from different dimensions.
% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
Firstly, since water resources are scarce, the most widespread concern is the rising stresses on human societies to use water resources.
Even though the stocks of water in artificial reservoirs are helpful to water resources availability, greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water utilization during the last century.
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018a, qinFlexibilityIntensityGlobal2019}
% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
Secondly, as the need of industrial and ecological developments, tendentiousness of water utilization changed with. 
Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths and preferential tendentiousness in the economy profits and water consumption regarding industry or services, leading potential conflicts between different sectors.
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}
% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
Thirdly, since water distribution and utilization are inherently basinal concerns, patterns of also play an important role.
% 全球总的取水量很少，但缺水地区很多
Although only 10\% of available water is withdrawn on global average, about 30\% of population live in highly water-stressed areas,
where dominated sectors of water utilization are various as well. 
\cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}
% 此外，人类活动还在改变这一格局
In addition, human activities are still changing this pattern, since positive impacts caused by human interventions mostly occur in upper regions whereas aggravated water resources downstream, in many basins around the world.
\cite{veldkampWaterScarcityHotspots2017}
% 将三种视角结合，就是“水资源利用体系”。
Although existing researches have evaluated the aspects of water resource utilization from these different dimensions, we still cannot obtain a coherent understanding of regime shifts regard to social development and water utilization, without integrating them.

% tag 讨论最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization.
% 使用案例研究
Then, by applying this index to the Yellow River Basin, China, we analysed water utilization regimes and their shifts in this typical basin of anthropogenic impacts, with change points detection and contribution decomposition methods following.
% 指出发展困局
In addition, combining data analysis, we identify causes of the regime shifts. 
% 最后总结出一般性框架
Finally, refer to the existing theories, we summarized a general transition framework of water utilization regimes, which can be a useful guideline for basins to predict development traps and to develop in a coordinated way.
